\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{\textbf{#1}{: #2 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeExpSubheading}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} --- #2 & #3 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\Large Nithyanand (Niranjan) Chandarraj} & \\
\href{https://bit.ly/nchandar}{bit.ly/nchandar} & Mobile: +1 (650) 238 7999 \\
\href{mailto:nniranc@gmail.com}{nniranc@gmail.com} & \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

  \resumeExpSubheading
    {Salesforce}{Software Engineering LMTS}{Jan 2024 -- Present}
    \resumeItemListStart
      \resumeItem{Platform Architecture}
        {Led backend architecture for Sales Coach, an AI-powered coaching platform for sales executives.}
      \resumeItem{AI Systems}
        {Designed RAG-based systems using Whisper (STT), BYOM (LLMs), and Amazon Polly (TTS).}
      \resumeItem{Scalable APIs}
        {Built low-latency APIs for real-time conversational coaching simulations and model interactions.}
      \resumeItem{Reliability and Extensibility}
        {Owned system reliability, extensibility, and integration readiness for future AI model upgrades.}
      \resumeItem{Salesforce Go}
        {Built backend and platform systems for intelligent setup experiences with guided, agent-assisted insights from licenses, features, and org configuration.}
      \resumeItem{Recommendations Engine}
        {Designed APIs and data pipelines that analyze entitlements and setup state to surface actionable admin recommendations.}
      \resumeItem{Technical Leadership}
        {Mentored engineers and influenced platform-level architecture and delivery decisions.}
    \resumeItemListEnd

  \resumeExpSubheading
    {Salesforce}{Software Engineering SMTS}{Oct 2018 -- Dec 2023}
    \resumeItemListStart
      \resumeItem{PRM Enablement APIs}
        {Designed and built backend APIs and services for the PRM Enablement platform, used by internal teams and external customers.}
      \resumeItem{Performance}
        {Implemented client-side caching using Lightning Data Service (LDS) to improve UI responsiveness and reduce redundant API calls.}
      \resumeItem{Real-Time Progress Updates}
        {Built event-driven milestone and task refresh flows using backend events and streaming/websocket channels so the UI reflects latest progress in near real time.}
      \resumeItem{Notifications}
        {Designed and delivered in-app and email notification services for PRM Enablement workflows.}
      \resumeItem{Platform Architecture}
        {Designed and built the In-App Guidance platform to improve feature adoption, onboarding, and end-user education.}
      \resumeItem{Prompting Model}
        {Developed both declarative and programmatic prompt capabilities for Salesforce customers at enterprise scale.}
      \resumeItem{Contextual Help}
        {Built the Smart In-App Contextual Help system end-to-end on the Lightning platform.}
      \resumeItem{Orchestration}
        {Implemented the prompt orchestration framework to coordinate delivery timing and targeting across user journeys.}
      \resumeItem{Technical Leadership}
        {Partnered with PRM teams on API adoption and mentored junior engineers across feature delivery and execution.}
    \resumeItemListEnd

  \resumeExpSubheading
    {Salesforce}{Software Engineering MTS}{Sep 2016 -- Sep 2018}
    \resumeItemListStart
      \resumeItem{Navigation \/ Services}
        {Designed and built customizable global navigation for multiple entity types, including bulk-operation service APIs.}
      \resumeItem{Focus Management}
        {Built Global Focus Manager to handle focus transitions across dynamic UI state changes; contributed to Aura framework components.}
      \resumeItem{Notifications and Favorites}
        {Implemented notification service APIs and PL/SQL logic for bulk read/seen status; built header and routing logic for Favorites.}
    \resumeItemListEnd

  \resumeExpSubheading
    {Salesforce}{Software Engineering AMTS}{Aug 2015 -- Aug 2016}
    \resumeItemListStart
      \resumeItem{Notifications Platform}
        {Contributed as a key engineer in building the Lightning notifications platform using CometD and Streaming API.}
      \resumeItem{Client Streaming}
        {Improved client-side streaming libraries for more consistent polling and data updates.}
      \resumeItem{Reusable Components}
        {Built reusable web components including Docked Composer and Notifications modules.}
    \resumeItemListEnd

  \resumeExpSubheading
    {Salesforce}{Software Engineering Intern}{May 2014 -- Aug 2014}
    \resumeItemListStart
      \resumeItem{Mobile Platform}
        {Built service APIs for offline priming in Salesforce1 and implemented client-side data store features using Java, JavaScript, and Aura.}
      \resumeItem{Testing}
        {Added unit, functional, and end-to-end test coverage for API and platform changes.}
    \resumeItemListEnd

  \resumeExpSubheading
    {Cognizant}{Programmer Analyst Trainee}{Sep 2012 -- May 2013}
    \resumeItemListStart
      \resumeItem{Internal Tools}
        {Developed internal tools using Java, COBOL, and DB2; collaborated with enterprise product teams.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\begin{itemize}[leftmargin=*,itemsep=0pt,topsep=1pt]
  \resumeExpSubheading
    {M.S. in Computing Science}{Simon Fraser University, Canada}{Sep 2013 -- Aug 2015}
  \resumeExpSubheading
    {B.E. in Computer Science}{Anna University, India}{Aug 2008 -- Mar 2012}
\end{itemize}

%--------SKILLS------------

\section{Skills}
\resumeSubHeadingListStart
\item \small{
  \textbf{Technologies}: Java, JavaScript, TypeScript, C, C++, HTML5, React,
CSS, Lua \\
  \textbf{Database}: SQL, PL/SQL, Postgres, MongoDB, DB2 \\
  \textbf{Other}: REST, RPC, Kafka, Redis, AJAX, XML, Spring MVC, Node,
Perforce, Git
}
\resumeSubHeadingListEnd

%-----------ACTIVITIES AND AWARDS-----------------
\section{Activities \& Awards}
\resumeSubHeadingListStart
  \resumeSubItem{Patent}{Targeting System For Web Page Components (US 11,442,754) -- \href{https://uspto.report/patent/grant/11,442,754}{link}}
  \resumeSubItem{Patent}{Implementing A User Engagement Platform Using A Database System (US 20200097477) -- \href{https://uspto.report/patent/app/20200097477}{link}}
  \resumeSubItem{Patent}{Creation and presentation of accessible targeted prompts (US 12,236,253 B2) -- \href{https://patents.google.com/patent/US12236253B2/en}{link}}
  \resumeSubItem{Community}{Conducted Salesforce bootcamps as SME in Java, JavaScript, and testing best practices}
  \resumeSubItem{Recognition}{Spot recognition for critical production outage recovery}
\resumeSubHeadingListEnd

\end{document}
